Make any stupid plot you want

### 2020-09-30 draft/intro.tex
notes on tau

>>>>

categorical & shapres have the group structure and so can do 
a $a: c \mapsto \s$
Optimal transform $a_{i}$ is one from a measurment space to a visual channel where both sides have the same group transforms-
because equivaraince requires having the same transforms on the same side.

artists take in class of visuals +

A - matplotlib artists 
$A: FB \mapsto CW$
$\tau: fb \mapsto vv $visual variable transformers
$\{\tau_{1}, \tau_{2}...\tau_{n}}(K)\mapsto {CW_{1}, CW_{2}, ...CW_{n}}$ 
$\mapsto$ is what embeds the topology k 
functions that know how to embed the k (mark)
functions that work on the fibers $\tau$

%% flip this to the otherside so it's an adjacency matrix
